---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{mappingEditr}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This app is meant to create a friendly interface to edit master lookup tables
in JSON format. The JSON format is standardized so it can be leveraged to 
automate the mapping process in data pipelines that reads data from non SDMX
sources and format them into SDMX

## Installation

You can install the development version of `{mappingEditr}` like so:

```{r}
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Run

You can launch the application by running:

```{r, eval = FALSE}
mappingEditr::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("mappingEditr")
```

```{r, error = TRUE}
covr::package_coverage()
```
